WORCS: A Workflow for Open Reproducible Code in Science

### 2020-11-17 paper/Manuscript_DS.Rmd
update 2020-11-17 11:54:27

When a project is conducted in a different software environment than `R`,
or if an R-project has external dependencies not tracked by `renv`,
then users might choose to use [Docker](https://www.docker.com/) for dependency management.  
Docker instantiates a "Docker container": An environment that behaves like a
virtual computer, which can be stored like a time capsule, and
identically reinstated on a user computer, or in the cloud.
Although the use of Docker falls outside of the scope of the present paper,
for existing users, a Docker build running `worcs` and its dependencies is available.
The [stetup with Docker vignette](https://cjvanlissa.github.io/worcs/articles/docker.html)
explains how to instantiate this build.
For more information on this topic,
@peikertReproducibleDataAnalysis2019 describe 
a Docker-based workflow for computational reproducibility that is
conceptually and practically compatible with WORCS.

@@

Before you can use the `R` implementation of the WORCS workflow,
you have to install the required software.
This 30 minute procedure is documented
in [the setup vignette](https://cjvanlissa.github.io/worcs/articles/setup.html).
After setting up your system, you can use `worcs` for all of your
projects.
Alternatively, Docker users can follow [the stetup with Docker vignette](https://cjvanlissa.github.io/worcs/articles/docker.html).
The `R` implementation of the workflow introduced earlier is detailed,
step-by-step, in
[the workflow vignette](https://cjvanlissa.github.io/worcs/articles/workflow.html).

>>>>

When a project is conducted in a different software environment than `R`,
or if an R-project has external dependencies not tracked by `renv`,
then users might choose to use [Docker](https://www.docker.com/) for dependency management.  
Docker instantiates a "Docker container": An environment that behaves like a
virtual computer, which can be stored like a time capsule, and
identically reinstated on a user computer, or in the cloud.
Although the use of Docker falls outside of the scope of the present paper,
for existing users, a Docker build running `worcs` and its dependencies is available.
The [stetup with Docker vignette](https://cjvanlissa.github.io/worcs/articles/setup-docker.html)
explains how to instantiate this build.
For more information on this topic,
@peikertReproducibleDataAnalysis2019 describe 
a Docker-based workflow for computational reproducibility that is
conceptually and practically compatible with WORCS.

@@

Before you can use the `R` implementation of the WORCS workflow,
you have to install the required software.
This 30 minute procedure is documented
in [the setup vignette](https://cjvanlissa.github.io/worcs/articles/setup.html).
After setting up your system, you can use `worcs` for all of your
projects.
Alternatively, Docker users can follow [the stetup with Docker vignette](https://cjvanlissa.github.io/worcs/articles/setup-docker.html).
The `R` implementation of the workflow introduced earlier is detailed,
step-by-step, in
[the workflow vignette](https://cjvanlissa.github.io/worcs/articles/workflow.html).

### 2020-11-17 paper/reviews_ds.Rmd
update 2020-11-17 11:54:27

---
title       : "Manuscript title"
authors     : "First Author & Second Author"
journal     : "Journal title"
manuscript  : "Manuscript number"

class       : "draft"
bibliography      : ["worcs.bib"]  
output      : papaja::revision_letter_pdf
---

@@

> Before you can use the `R` implementation of the WORCS workflow,
you have to install the required software.
This 30 minute procedure is documented
in [the setup vignette](https://cjvanlissa.github.io/worcs/articles/setup.html).
After setting up your system, you can use `worcs` for all of your
projects.
Alternatively, Docker users can follow [the stetup with Docker vignette](https://cjvanlissa.github.io/worcs/articles/docker.html).

>>>>

---
title       : "WORCS: A Workflow for Open Reproducible Code in Science"
authors     : |
    [Caspar J. Van Lissa](c.j.vanlissa@uu.nl),
    Andreas M. Brandmaier,
    Loek Brinkman,
    Anna-Lena Lamprecht,
    Aaron Peikert,
    Marijn E. Struiksma, &
    Barbara Vreede
journal     : "Data Science"

class       : "draft"
bibliography      : ["worcs.bib"]  
output      : papaja::revision_letter_pdf
urlcolor          : blue
---

@@

> Before you can use the `R` implementation of the WORCS workflow,
you have to install the required software.
This 30 minute procedure is documented
in [the setup vignette](https://cjvanlissa.github.io/worcs/articles/setup.html).
After setting up your system, you can use `worcs` for all of your
projects.
Alternatively, Docker users can follow [the stetup with Docker vignette](https://cjvanlissa.github.io/worcs/articles/setup-docker.html).
